Evolution of Processes in Delivering Reliable Software in the European Scientific Arena

### 2018-06-28 paper-ieee-trans.tex

\bibitem{campana-atlas}
S. Campana  \emph{et al.},
``Analysis of the ATLAS Rome production experience on the LHC computing grid,''
\emph{IEEE 1st International Conference of e-Science and Grid Computing},
pp. 8-pp, 2005.

@@

\bibitem{datagrid}
L. Momtahan and A. Martin,
``e--Science Experiences: Software Engineering Practice and the EU DataGrid,''
in \emph{Ninth Asia--Pacific Software Engineering Conference},
pp. 269--275, Dec. 2002.

>>>>

\bibitem{campana-atlas}
S. Campana  \emph{et al.},
``Analysis of the ATLAS Rome production experience on the LHC computing grid,''
\emph{IEEE 1st Int. Conf. of e-Science and Grid Computing},
pp. 8-pp, 2005.

@@

\bibitem{datagrid}
L. Momtahan and A. Martin,
``e--Science Experiences: Software Engineering Practice and the EU DataGrid,''
in \emph{9th Asia--Pacific Softw. Eng. Conf.},
pp. 269--275, Dec. 2002.
